\chapter{Motivation}
I have many network services that run in my home.  Many of them are
services I've created myself from scratch in C++.  If a service
can be secured and strongly authenticated, it should be.  That's the
case for everything I've authored that runs in my home.  My garage
door opener (mcpigdo), my firewall software (mcblockd), my network
and host monitoring software (mcrover), my weather server
(mcweatherd), my RDAP server (dwmrdapd), etc.

Note that many of these services need to work without any user
interaction.  Hence I don't need my keys to be protected by passwords,
and at the moment I don't support password-protected keys in KeyStash.

For years I used Crypto++ for encryption and proof of identity, via my
own libDwmAuth library.  But a couple of years ago I found some
problems in Crypto++ that I reported to the maintainers but were never
fixed.  The issues I reported were memory leaks, and also corruption
on some platforms (Raspbian).  Despite me explaining what I considered
obvious (just from code review), the problems were not fixed.

So I've given up on Crypto++.  Not the end of the world, especially
since what I need is much smaller than what Crypto++ provides.
I need Ed25519 key support for signatures and XChaCha20Poly1305
for AEAD encryption (though I'm not supporting the additional data
at the moment).  libsodium, despite being a C library with some
awkward overhead when interfacing with C++ strings, easily fits
the bill.

Basically, I needed to replace libDwmAuth (which used Crypto++) with
a new library that utilizes libsodium instead.
